### 2011-07-01 Posters/NNS2011/myposter.tex
DOC: added bibs

\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{bm}

@@

\newlength{\leftimgwidth}
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=colorf,
  bgColorTwo=white,
  borderColor=colorK,
  headerColorOne=colork,
  headerColorTwo=white,
  headerFontColor=colorM,
  boxColorOne=white,
  boxColorTwo=colorC,
  % Format of textbox
  textborder=roundedleft,
%  textborder=rectangle,
  % Format of text header
  eyecatcher=no,
  headerborder=closed,
  headerheight=0.11\textheight,
  headershape=roundedright,
  headershade=shade-lr,
  headerfont=\Large, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {\includegraphics[width=10em]{D1077}} % No eye catcher for this poster. (eyecatcher=no above). If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  { %Sans Serif
  %\bf% Serif
  Multivariate analysis of diffusion tensor imaging and cortical thickness maps in a traumatic brain injury (TBI) cohort using Advanced Normalization Tools (ANTs)
  \vspace{0.1em}}
  % Authors
  { %Sans Serif
  % Serif
  Nicholas J. Tustison$^1$, Brian B. Avants$^2$, Philip A. Cook$^2$, Junghoon Kim$^3$, John Whyte$^3$, James C. Gee$^2$, Stephen  Ahlers$^4$, James R. Stone$^1$ \newline
  % Affiliations
  {\normalsize $^1$University of Virginia, $^2$University of Pennsylvania, $^3$Rehabilitation Research Institute, $^4$Naval Medical Research Center \\
  P309
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Diffuse Traumatic Brain Injury Data}{name=data,column=0,below=introduction}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The TBI data used in this study is part of a larger effort investigating 
the relationship between various neuroimaging indices and cognitive and 
functional abilities in long-term survivors of TBI (principal 
investigator: John Whyte).   
\paragraph{Description of cohort: }
17 controls and 16 patients with TBI were used.  
Each patient had a history of non-penetrating traumatic brain injury 
of at least moderate severity defined by significant and well-documented
loss or alteration of consciousness following injury in addition to meeting
several other exclusionary criteria.  The healthy volunteers were matched in terms of age, gender, ethnicity, handedness, and years of education.
\paragraph{Image acquisition:} 
High resolution T1-weighted anatomic images were obtained using a 3D MP-RAGE 
imaging sequence with the following acquisition parameters: TR = 1620 ms, 
TI = 950 ms, TE = 3 ms, flip angle = 15$^\circ$, 160 contiguous slices of 
1.0 mm thickness, FOV = 192 $\times$ 256 mm$^2$, matrix = 192 $\times$ 256, 
1NEX with a scan time of 6 minutes, and voxel size = 1 mm$^3$.  30-directional
DTI images were also obtained.

@@

\begin{center}
{\bf Statistics}\\
\vspace{4mm}
\begin{tabular}{c}
\includegraphics[height=25mm]{MUvPSCCAN.pdf} \\
sparse canonical correlation analysis \cite{Avants2010b}
\end{tabular}
\end{center}

\smaller
\begin{center}
  http://wwww.picsl.upenn.edu/ANTs
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{ANTs TBI Multivariate Processing Workflow}{name=workflow,column=1,span=2}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{0.3em}

\begin{center}
\begin{tabular}{c}
\includegraphics[height=80mm]{workflow.pdf} 
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}{name=results,column=1,span=1,below=workflow}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{0.3em}
  }

@@

 SCCA demonstrates significant differences between the control and patient groups in both the FA ($p < 0.002$) and gray matter ($p < 0.01$)	that	are	widespread	but	largely	focus	on	thalamocortical networks related to the limbic system. Specific regional differences in- cluded the medial thalamic nuclei, hypothalamus, amygdala, hippo- campus, anterior cingulate cortex, orbitofrontal cortex and fornix. Using these SCCA-identified regions, we demonstrate a strong correlation of the degree of injury in WM and GM within the patient group.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{References}{name=references,column=2,below=workflow}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \smaller

      \vspace{-0.4em}
      \renewcommand{\refname}{\vspace{-0.8em}}
      \bibliographystyle{abbrv}
      \bibliography{references}

>>>>

\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{bm}

@@

\newlength{\leftimgwidth}
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=colorf,
  bgColorTwo=white,
  borderColor=colorK,
  headerColorOne=colork,
  headerColorTwo=white,
  headerFontColor=colorM,
  boxColorOne=white,
  boxColorTwo=colorC,
  % Format of textbox
  textborder=roundedleft,
%  textborder=rectangle,
  % Format of text header
  eyecatcher=no,
  headerborder=closed,
  headerheight=0.11\textheight,
  headershape=roundedright,
  headershade=shade-lr,
  headerfont=\Large, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {\includegraphics[width=10em]{D1077}} % No eye catcher for this poster. (eyecatcher=no above). If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  { %Sans Serif
  %\bf% Serif
  Multivariate analysis of diffusion tensor imaging and cortical thickness maps in a traumatic brain injury (TBI) cohort using Advanced Normalization Tools (ANTs)
  \vspace{0.1em}}
  % Authors
  { %Sans Serif
  % Serif
  Nicholas J. Tustison$^1$, Brian B. Avants$^2$, Philip A. Cook$^2$, Junghoon Kim$^3$, John Whyte$^3$, James C. Gee$^2$, Stephen  Ahlers$^4$, James R. Stone$^1$ \newline
  % Affiliations
  {\normalsize $^1$University of Virginia, $^2$University of Pennsylvania, $^3$Moss Rehabilitation Research Institute, $^4$Naval Medical Research Center \\
  P309
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Diffuse traumatic brain injury data}{name=data,column=0,below=introduction}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The TBI data used in this study is part of a larger effort investigating 
the relationship between various neuroimaging indices and cognitive and 
functional abilities in long-term survivors of TBI (principal 
investigator: John Whyte).   
\paragraph{Description of cohort: }
17 controls and 16 patients with TBI were used.  
Each patient had a history of non-penetrating traumatic brain injury 
of at least moderate severity defined by significant and well-documented
loss or alteration of consciousness following injury in addition to meeting
several other exclusionary criteria.  The healthy volunteers were matched in terms of age, gender, ethnicity, handedness, and years of education.
\paragraph{Image acquisition:} 
High resolution T1-weighted anatomic images were obtained using a 3D MP-RAGE 
imaging sequence with the following acquisition parameters: TR = 1620 ms, 
TI = 950 ms, TE = 3 ms, flip angle = 15$^\circ$, 160 contiguous slices of 
1.0 mm thickness, FOV = 192 $\times$ 256 mm$^2$, matrix = 192 $\times$ 256, 
1NEX with a scan time of 6 minutes, and voxel size = 1 mm$^3$.  30-directional
DTI images were also obtained.

@@

\vspace{-6mm}

\begin{center}
{\bf Multivariate analysis using SCCA}\\
\end{center}
\vspace{-1mm}
Sparse canonical correlation analysis (SCCA) adapts classical CCA to
situations where the number of predictors is much greater than the number
of subjects for inference of correlative relationships between different
``views'' of some underlying phenomenon. For gray matter density ($\mathbf{G}$) and
DTI-derived FA  ($\mathbf{F}$) views, SCCA solves the following
criterion \cite{Avants2010b}:
\vspace{-7mm}
\begin{center}
\begin{align*}
\underset{\omega_{\mathbf{G}}, \omega_{\mathbf{F}}}{\operatorname{argmax}} \left\{\omega_{\mathbf{G}} \mathbf{G}^\mathrm{T}\mathbf{F}\omega_{\mathbf{F}} - \lambda_{\mathbf{G}}\sum_{v_{\mathbf{G}}} |\omega_{\mathbf{G}}|_1 - \lambda_{\mathbf{F}}\sum_{v_{\mathbf{F}}} |\omega_{\mathbf{F}}|_1\right\}: \|\omega_{\mathbf{G}}\|, \|\omega_{\mathbf{F}}\| \leq 1.
\end{align*}
\end{center}

%\smaller
%\begin{center}
%  http://wwww.picsl.upenn.edu/ANTs
%\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Materials and methods:  ANTs subject and template processing}{name=workflow,column=1,span=2}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{0.3em}

\begin{center}
\begin{tabular}{p{11cm}p{11cm}}
{\makebox[11cm][c]{\bf Individual subject processing}\vspace{-3mm} } & 
{\makebox[11cm][c]{\bf Template generation}} \\
{\makebox[11cm][c]{\includegraphics[height=60mm]{individualProcessing.pdf}}}\vspace{3mm} &
{\makebox[11cm][c]{\includegraphics[height=60mm]{templateBuilding.pdf}}} \\
\small Processing of each anatomical (T1-weighted) image consists of the
following steps: 
\begin{itemize}
  \item bias correction,
  \item skull stripping using Atropos coupled with anatomical priors, and
  \item prior-based csf, white matter, and gray matter segmentation.  The
  latter yields the gray matter density image for each subject.
\end{itemize}
FA images are mapped to each anatomical image using the transform
obtained from registration of the average diffusion image to the 
corresponding T1. 
& 
\small Statistical analysis requires normalization to a standard space provided
by the total template.  All 17 controls and all 16 TBI patients were used
to generate their respective unbiased templates.  These two templates were then
used to generate the final/standard template.  Thus the mapping from the individual 
gray matter density (GMD) image to the total template is given by
\begin{align*}
  \mathrm{GMD}_{subject}\,\,\mathbf{Id}\,\, \mathrm{T1}_{subject}\leadsto \mathrm{template}_{population}\leadsto \mathrm{template}_{total}.
\end{align*}
Similarly, the mapping for each subject's FA image to the total template is given
by the 
transform composition
\begin{align*}
  \mathrm{FA}_{subject}\rightarrow\mathrm{T1}_{subject}\leadsto \mathrm{template}_{population}\leadsto \mathrm{template}_{total}.
\end{align*}
\\
\end{tabular}
\end{center}

\vspace{-10mm}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Multivariate analysis results}{name=results,column=1,span=2,below=workflow}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{0.3em}

\begin{center}
\begin{tabular}{p{6cm}cc} \vspace{-70mm}
{\makebox[6cm][c]{\includegraphics[height=50mm]{scca.pdf} }} \
\small The significant correlations derived from the GMD/FA views
vs. diagnostic view provide significant regions for finding
correlations between GMD and FA. & {           } &
{\includegraphics[height=80mm]{results.pdf}}
\end{tabular}
\end{center}

@@

@@

 SCCA demonstrates significant differences between the control and patient groups in both the FA ($p < 0.002$) and gray matter ($p < 0.04$)	that	are	widespread	but	largely	focus	on	thalamocortical networks related to the limbic system. Specific regional differences included the medial thalamic nuclei, hypothalamus, amygdala, hippocampus, anterior cingulate cortex, orbitofrontal cortex and fornix. Using these SCCA-identified regions, we demonstrate a strong correlation ($p < 0.08$) of the degree of injury in WM and GM within the patient group.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{References}{name=references,column=2,below=results,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.3em}
    \scriptsize
      \vspace{-0.4em}
      \renewcommand{\refname}{\vspace{-0.8em}}
      \bibliographystyle{abbrv}
      \bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Open source software}{name=software,column=1,below=conclusions,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{1mm}
  \begin{center}
  \begin{tabular}{cc}
  \includegraphics[height=18mm]{ants_logo.png} &
  \includegraphics[height=18mm]{itkLogo.jpg} \\
%  {Advanced Normalization Tools} & {Insight Toolkit} \\
  {\tiny http://www.picsl.upenn.edu/ANTs} &
%  {\tiny http://www.cs.ucl.ac.uk/research/medic/camino} &
  {\tiny http://www.itk.org/} \\
  \end{tabular}
  \end{center}

@@
